---
title: "HW 1"
subtitle: "Data 180, Professor Kennedy"
author: 
  name: "Tom Gehman"
  email: "gehmand@dickinson.edu"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document
---

20/20.  good job Tom. This is excellent work.

Make sure that you have accepted the hw invitation link, and working with your clone repository.

**Due date:** September 21 beginning of class.

**Reminder:** You can insert R code in your Rmd file as a chunk in the following way:
```{r}
# Your code goes here
```
Make sure to insert a chunk for each (sub)section of the assignment.

## Preliminary Task
Go to [datacamp.com](https://datacamp.com) and complete the tutorial "Introduction to R".


## Task 1
a) Store the data below in a data frame object named `my_df`.

|Person | Preference|
|:------|:----------|
|Alice | Twitter |
| Bob | Facebook |
| Charlie | Twitter |
| Denise | Instagram |
| Erin | Facebook |
| Frank | Twitter |
| Gisele | Twitter |
| Harry | Instagram |

```{r}
my_df = data.frame(
  Person = c("Alice", "Bob", "Charlie", "Denise", "Erin", "Frank", "Gisele", "Harry"), 
  Preference = c("Twitter", "Facebook", "Twitter", "Instagram", "Facebook", "Twitter", "Twitter", "Instagram")
)

```

b) What are the dimensions of `my_df`?

```{r}
#The dimensions of my_df are 8x2. 
print(dim(my_df))
```
c) Write R code that counts the total number of users.

```{r}
#length of Person column of my_df
print(length(my_df$Person))
```

d) Write R code that counts the total number of users who prefer Twitter.

```{r}
#create boolean vector using condition that Preference=="Twitter"
twitters = my_df$Preference=="Twitter"
#print(twitters)

#use boolean vector to index People and store them as a vector, overwriting the first vector
twitters = my_df$Person[twitters]
#print(twitters)

#Length of vector of people
print(length(twitters))
```

e) Write R code that returns what Gisele prefers.

```{r}
#which() returns index(es) of my_df$Person when the element =="Gisele"
#index is then used to index my_df$Preference and identify the corresponding preference
#I could've used the same method as in part d, but I wanted to try this since it's more concise.  
my_df$Preference[which(my_df$Person=="Gisele")]

```

## Task 2
a) Create a vector named `my_vec` that includes all integers from 1 to 10 (inclusive).
```{r}
my_vec = 1:10
```
b) Replace the second element in `my_vec` with the number `99`.
```{r}
my_vec[2]=99
#print(my_vec)
```
c) Write a function called `my_func` that prints `This element is greater than 5!` if an element in `myvec` is greater than 5, and `This element is NOT greater than 5!` otherwise.
```{r}
my_func = function(index) {#index is the index of my_vec to compare
  if (my_vec[index]>5){
    print("This element is greater than 5!")
  } else {
    print("This element is NOT greater than 5!")
  }
}
#example function calls to test my_func()
# my_func(1)
# my_func(2)
# my_func(5)
# my_func(9)
```

## Task 3
a. Write a function named `get_fibonacci` that returns the n'th value in the [fibonacci sequence](https://www.mathsisfun.com/numbers/fibonacci-sequence.html). For example, `get_fibonacci(5)` should return 3; `get_fibonacci(7)` should return 8 and so on. ***Hint:** It is possible to call the same function from inside it. E.g., you can call `get_fibonacci()` from inside `get_fibonacci()`. Like inception!*

```{r}
get_fibonacci = function(term, seed1=0, seed2=1){#optional arguments are only used when the function calls itself.  
  if (term==1){#return 0 for first term
    return(0)
  } else if (term>3){
    #term-1 allows function to count down and repeat for the number of terms
    #seed1 and seed2 represent the previous two numbers in the sequence as the function calculates the next one.  
    #seed2 becomes the next seed1, and seed1+seed2 becomes the next seed2
    get_fibonacci(term-1, seed2, seed1+seed2)
  } else { #after a number of repeats, terms no longer is >3, signalling that the function is ready to return the final value.  
    return(seed1+seed2)
  }
}

#testing values
# get_fibonacci(1)
# get_fibonacci(2)
# get_fibonacci(3)
# get_fibonacci(4)
# get_fibonacci(5)
# get_fibonacci(6)
# get_fibonacci(7)

```


b. Using your function in part (a), find and return the 19th value in the fibonacci sequence.
```{r}
get_fibonacci(19)
```


<br>
You are done! 🏁 Don't forget to `commit` and `push` your .Rmd file to your Github clone repository before the due date.
<br>

